---
title: "LandR_MPB_studyArea"
author: "achubaty"
date: "20 April 2021"
output: 
  html_document: 
    keep_md: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = "hold")
```

# Overview

Provide an overview of what the module does / how to use the module.

Module documentation should be written so that others can use your module.
This is a template for module documentation, and should be changed to reflect your module.

## R Markdown

R Markdown syntax allows R code, outputs, and figures to be rendered in the documentation.

For help writing in R Markdown, see https://rmarkdown.rstudio.com/.

# Usage

```{r module_usage}
library(SpaDES.core)

setPaths(modulePath = file.path("~/GitHub"))
getPaths() # shows where the 4 relevant paths are

times <- list(start = 0, end = 1)

parameters <- list(
  LandR_MPB_studyArea = list(
    .plotInitialTime = 1
  )
)
modules <- list("LandR_MPB_studyArea")
objects <- list()
inputs <- list()
outputs <- list()

mySim <- simInit(times = times, params = parameters, modules = modules,
                 objects = objects)

mySimOut <- spades(mySim)
```

# Parameters

Provide a summary of user-visible parameters.

```{r moduleParams, echo = FALSE}
df_params <- moduleParams("LandR_MPB_studyArea", "~/GitHub")
knitr::kable(df_params)
```

# Events

Describe what happens for each event type.

## Plotting

Write what is plotted.

## Saving

Write what is saved.

# Data dependencies

## Input data

How to obtain input data, and a description of the data required by the module.
If `sourceURL` is specified, `downloadData("LandR_MPB_studyArea", "~/GitHub")` may be sufficient.

```{r moduleInputs, echo = FALSE}
df_inputs <- moduleInputs("LandR_MPB_studyArea", "~/GitHub")
knitr::kable(df_inputs)
```

## Output data

Description of the module outputs.

```{r moduleOutputs, echo = FALSE}
df_outputs <- moduleOutputs("LandR_MPB_studyArea", "~/GitHub")
knitr::kable(df_outputs)
```

# Links to other modules

Part of the Mountain Pine Beetle Red Top Growth Model, which evaluates short-run potential for MPB establishment, eruption, and spread.

- `mpbMassAttacksData`
- `mpbClimateData`
- `mpbPine`
- `mpbRedTopSpread`

Future linkages include the `LandR` Biomass suite of modules to simulate/forecast forest vegetation dynamics, and the `fireSense` wildfire simulation model.

